Network Cascades

### 2016-08-23 paper/paper.tex
Start describing cascade condition stuff

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

@@

Now the model is simulated over a time $t$, starting with $0$. At a random point in time, the state of a single node is changed to $1$. This is analogous to the first person starting to use the application.

@@

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{csquotes}

@@

Now the model is simulated over a time $t$, starting with $0$. At a random point in time, the state of a single node (the seed) is changed to $1$. This is analogous to the first person starting to use the application.

@@

\section{Cascade Condition}\label{sec:section}

Watts claims that global cascades are only possible if \textquote{the largest vulnerable cluster percolates}. This is called the \emph{cascade condition}.

A node is vulnerable if its threshold is low enough so that only one of it's neighbors needs to switch state for it to switch state itslef. Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''. A vulerable cluster is a connected set of nodes that all switch state if a contained ``early adopter'' adjacent to an ``innovator'' switches its state. This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.
